\documentclass[]{article}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{tikz, amsmath, amssymb, bm, color}
\usepackage{geometry}
\usetikzlibrary{calc}
\usetikzlibrary{shapes,arrows}
\usepackage{todonotes}
\usepackage[american]{circuitikz}
\usepackage{pgfplots}
\usepackage{epstopdf}
\usepackage{listings}
%\usepackage{blochsphere}
\usepackage{datetime}
\usepackage{subcaption}
\usepackage{float}
\usepackage{cleveref}

\newenvironment{custom_itemize}{
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}


%\usepackage{multicol} % Used for the two-column layout of the document


%\usepackage{bm}


\title{Report Thesis}
\author{Kees Kroep 4246373}


\begin{document}

%  \twocolumn[{%% \begin{@twocolumnfalse}
  \maketitle
%   \end{@twocolumnfalse}
% }]

\newdate{M1}{25}{04}{2017}
\newdate{M2}{2}{05}{2017}
\newdate{M3}{9}{05}{2017}
\newdate{M4}{23}{05}{2017}
\newdate{M5}{30}{05}{2017}
\newdate{M6}{04}{07}{2017}
\newdate{M7}{18}{07}{2017}


\section{Milestones}

\textit{\date{\displaydate{M1}}}\\
\textbf{Installing and setup of hardware/software}\\
Set-up cadence with the TSMC40 nm tools. Set-up liberty, and calculate the files for a single library component.
I should familiarize myself with the design tools, partially helped by Alex to kickstart me.\\
\\
\textit{\date{\displaydate{M2}}}\\
\textbf{Running liberty through a subset of desired components and settings}\\
Depending on how automized the process is, this part should be easy but time consuming \\
\\
\textit{\date{\displaydate{M3}}}\\
\textbf{Analyze the first subset for performance translation}\\
Analyze the consistency of performance changes for different components, and try to spot trends. This can also be backed up by a literature study and some math. While doing this continue to calculate the remaining components in liberty\\
\\
\textit{\date{\displaydate{M4}}}\\
\textbf{Finish up analysis of entire set and present findings}\\
Go through the entire set where deemed necessary and draw conclusions. Based on findings construct presentation to present observations and design recommendations to discuss with coolgroup\\
\\
\textit{\date{\displaydate{M5}}}\\
\textbf{Implement feedback in analysis where required}\\
Depending on how well the work went, this should take a smaller time\\
\\
\textit{\date{\displaydate{M6}}}\\
\textbf{Design a test IC (schematic), to verify library}\\
Design a digital IC component to test out the new library. This component could somewhere between a fucntional system or a ring oscillator farm.\\
\\
\textit{\date{\displaydate{M7}}}\\
\textbf{Design a test IC (layout)}\\
Make the layout for the test IC. 
\\
\textit{Future}\\
\textbf{Make components for the QC}\\
Make components for the qunatum computer where required while making use of my own library and the recommendations accompanying it.



\end{document}
